Rapid slip-deficit rates at the eastern margin of the Tibetan plateau prior to the 2008 $\textrm{M}_\textrm{w}$ 7.9 Wenchuan earthquake

### 2014-11-14 paper.tex
Slight typo edits.

The velocity gradient across the Longmen Shan rangefront is negligible (Figure \ref{fig:big_stack}a). To fit these observed, any planar or listric geometry with interseismic locking limited to the range-front (for example, a Beichuan-only fault geometry) would require near-zero slip-deficit rates. Such a model is inconsistent with slip during the Wenchuan earthquake on the Beichuan and Penguan faults and significant geologic estmates of shortening \citep{Hubbard2010, Li2010, Wang2013, Wang2014}, and . It is also inconsistent with co- and post-seismic slip on the detachment \citep{Qi2011, Fielding2013b}.

>>>>

The velocity gradient across the Longmen Shan rangefront is negligible (Figure \ref{fig:big_stack}a). To fit these observed near-field data, any planar or listric geometry with interseismic locking limited to the range-front (for example, a Beichuan-only fault geometry) would require near-zero slip-deficit rates. Such a model is inconsistent with slip during the Wenchuan earthquake on the Beichuan and Penguan faults and with geologic estimates of significant shortening \citep{Hubbard2010, Li2010a, Wang2013, Wang2014}. It is also inconsistent with co- and post-seismic slip on the detachment \citep{Qi2011, Fielding2013b}.
